[DRAFT] Tipologi Kerentanan Iklim pada Penghidupan Berbasis Pertanian: Kabupaten Bone

### 2023-11-09 draft_fgd_tipologi_kerentanan_bone.qmd
Update draft_fgd_tipologi_kerentanan_bone.qmd

```{r komposisi kecamatan}
#| warning: false
#| message: false
source("R/functions.R")
intisari_desk_kec <- readr::read_csv("data/interpretasi_tipologi_sulsel_id.csv") |> 
  dplyr::mutate(`Kepadatan RT` = `Luas (Ha)`/`Rumah Tangga`) |> 
  mutate(color_pal = c("#A65628","#E41A1C", "#377EB8",  "#4DAF4A","#FF7F00", "#984EA3", "black" ))

>>>>

```{r komposisi kecamatan}
#| warning: false
#| message: false
source("R/functions.R")
intisari_desk_kec <- readr::read_csv("data/interpretasi_tipologi_bone.csv") |> 
  dplyr::mutate(`Kepadatan RT` = `Luas (Ha)`/`Rumah Tangga`) |> 
  mutate(color_pal = c( "#377EB8","#E41A1C","#FF7F00" ,  "#4DAF4A", "black" ))
